% Part 3: References
\chapter*{References}

\begin{enumerate}

\item L. M. Saunders, ``Numerical Solution of the Flow Field in the Throat Region of a Nozzle,'' Brown Engineering Co. report BSVD-P-66-TN-001 (NASA CR 82601), August 1966.

\item R. F. Cuffel, L. H. Back, and P. F. Massier, ``Transonic Flow-Field in a Supersonic Nozzle with Small Throat Radius of Curvature,'' \textit{AIAA J.} 7, 1364--1366, July 1969.

\item A. A. Migdal, E. J. Wuchina, and W. D. Boyd, ``Method for Predicting the Nozzle Operating Line,'' NASA Lewis Research Center Report NASA CR-72547, April 1968.

\item S. Prozan, ``Numerical Solution of Transonic Flow in a Nozzle,'' Grumman Aircraft Engineering Corporation Report, 1966.

\item C. W. Laval, ``Calculation of Two-Dimensional Compressible Flow in Convergent-Divergent Channels,'' AEDC Report TR-69-120, August 1969.

\item P. Serra, ``Numerical Simulation of the Transonic Flow in a Convergent-Divergent Nozzle,'' CNES Report, 1970.

\item C. A. Brown and H. Ozcan, ``Numerical Solution of Steady Flow in a Nozzle,'' Douglas Aircraft Report, 1969.

\item R. W. MacCormack, ``The Effect of Viscosity in Hypervelocity Impact Cratering,'' AIAA Paper 69-354, 1969.

\item G. Moretti and M. Abbett, ``A Time-Dependent Method for the Analysis of Transonic Flows,'' \textit{AIAA J.} 4, 2136--2141, December 1966.

\item G. Moretti, ``Transonic and Supersonic Flow Computations,'' \textit{Advances in Applied Mathematics} 2, 1981.

\item J. von Neumann and R. D. Richtmyer, ``A Method for the Numerical Calculation of Hydrodynamic Shocks,'' \textit{J. Applied Phys.} 21, 232--237, March 1950.

\item \textit{Ibid}, Reference 11.

\item M. C. Cline, ``NAP: A Computer Program for the Computation of Two-Dimensional, Time-Dependent, Inviscid Nozzle Flow,'' Los Alamos Scientific Laboratory Report, 1977.

\item R. E. Loh and R. L. Loh, ``A Comparison of Computer Execution Times,'' TRW Technical Report, 1975.

\item IBM Corporation, ``System/360 Performance Characteristics,'' IBM Technical Manual, 1971.

\item R. H. Prozan and D. E. Kooker, ``Numerical Analysis of Steady Nozzle Flow Using Relaxation Methods,'' AIAA Paper, 1971.

\item T. P. Thornock, ``Experimental Study of Converging Nozzle Flow,'' NASA Technical Memorandum, June 1968.

\item D. L. Bresnahan and A. L. Johns, ``Experimental Flow in a Plug Nozzle,'' NASA Contractor Report, 1972.

\end{enumerate}

\addcontentsline{toc}{chapter}{References}
