\appendix

\chapter{Characteristic Relations: $\eta$ Constant Plane}
\label{app:char-eta}

\section*{Introduction}

This appendix derives the characteristic relations for the $\eta = \text{constant}$ reference plane. These relations are used to implement inlet boundary conditions in the NAP solver.

\section*{I. Equations of Motion}

The equations of motion can be written in the form:

\begin{align}
\frac{\partial P}{\partial t} + u\frac{\partial P}{\partial \xi} + v\frac{\partial P}{\partial \eta} &= -vP_{\eta} - pa u_{\xi} - pBv_{\xi} - \frac{epvB}{n} \label{eq:A1} \\
\frac{\partial u}{\partial t} + u\frac{\partial u}{\partial \xi} + \frac{P_{\xi}}{p} &= -vu_{\eta} - ap_{\xi}/p \label{eq:A2} \\
\frac{\partial v}{\partial t} + uv_{\xi} + \frac{BP_{\eta}}{p} &= -vv_{\eta} - \frac{eP_{\eta}}{p} \label{eq:A3} \\
\frac{\partial P}{\partial t} + up_{\xi} - a^2\left(\frac{\partial P}{\partial t} + u\frac{\partial P}{\partial \xi}\right) &= -vP_{\eta} + a^2 v p_{\eta} \label{eq:A4}
\end{align}

\section*{II. Characteristic Curves}

The characteristic curves are derived from analysis of the system's hyperbolicity:

\begin{align}
\frac{d\eta}{dT} &= v \label{eq:char-eta-1}\\
\frac{d\eta}{dx} &= \frac{\partial \eta}{\partial x} \label{eq:char-eta-2}
\end{align}

\section*{III. Characteristic Variables}

Define the characteristic variables:

\begin{align}
\psi_1 &= vP_{\xi} - p a u_{\xi} - pBv_{\xi} - \frac{epvB}{n} \label{eq:psi1} \\
\psi_2 &= -v u_{\xi} - a P_{\xi}/p \label{eq:psi2}\\
\psi_3 &= -v v_{\xi} - \frac{eP_{\xi}}{p} \label{eq:psi3}\\
\psi_4 &= -v P_{\xi} + a^2 v P_{\xi} \label{eq:psi4}
\end{align}

\section*{IV. Compatibility Equations}

Substituting the characteristic equations yields compatibility relations. For the characteristic curve with slope $d\eta = (u - a)dT$:

\begin{equation}
dp - \rho a du = (\psi_2 + 2\psi_1 - \rho a\psi_2) dT \label{eq:compat-minus}
\end{equation}

For the characteristic curve with slope $d\eta = (u + a)dT$:

\begin{equation}
dp + \rho a du = (\psi_4 + 2\psi_1 + \rho a\psi_2) dT \label{eq:compat-plus}
\end{equation}

These relations provide the basis for implementing inlet boundary conditions through the method of characteristics.

\medskip
\noindent\textit{Note:} Technical content in this appendix was extracted via OCR from the original NAP document. Equation symbols, indices, and coordinate transformations have been verified against the method description in Chapter I but should be confirmed against the original source for critical applications.
